% !TEX root = ..\proposal.tex

\section{Introduction}
    \label{sec:intro}



People often seek investment vehicles as a method to expand their savings, diversify their savings portfolio and grow their wealth. Several investment vehicles are available for investors to achieve the goals of diversification and value creation such as bonds, stocks, options, and derivatives. Each of these requires extensive skills and domain knowledge to master. Given the focus on stock market within the spectrum of this project, our aim is to advance the skill sets of our users to ensure that stock trading risks are properly acknowledged and appreciated. 

Traditionally, stock trading and investing in public companies was considered exclusive to high-value portfolios. Such accounts historically had a dedicated broker who communicated the buying and selling of stocks (orders) over the phone. With the advancement of technology, exchange mediums have become readily available from the convenience of a person's computer, tablet, or even smartphone. Technological advancement has opened the doors for many new investors and traders to enter the world of stock investing, though they are often lured in by marketing campaigns for particular products and `get rich quick’ schemes. The stock market can be an endless maze for new traders who are often lost in the labyrinth of technical terms and financial lingo. Additionally, high frequency trading has put the retail traders/trading at a disadvantage against huge machines and servers which trade at the microsecond-level using advanced analysis based on market changes, data releases, and news sentiment. This creates yet another barrier for the retail traders who are already hesitant so they might miss the chance of learning about the stock market or, on the other end of the spectrum, are under the impression that the stock market is a money making machine, resulting in uninformed and high risk investments.

To combat the aforementioned hurdles that retail traders often faced, we aim to create a virtual market ecosystem allowing traders and investors access to a unique experience that mimics the real stock exchange medium with virtual money. The user is given a set amount of virtual money to simu-buy or simu-sell shares (and potentially cryptocurrency) in order to test the investment strategy rather than risking the user’s own capital. The virtual market allows the users to evaluate the decisions taken in the short and long term by measuring portfolio yield in terms of absolute return and relative return. Our platform will allow traders to avoid falling into the marketing gimmicks and false advertisements by enabling them to test an investment strategy before real capital is at risk. This lets our users make better and more informed decisions about their chosen strategy, allowing them to accurately judge whether they need more knowledge or training prior to investing their hard-earned money into the stock market.
